A Simple Ratio for Estimating the Effective Reproduction Value of an Epidemic

### 2021-01-16 docs/manuscript/manuscript.Rmd
moved variable for proper compiling

>>>>

```{r}
# Descriptive Statistics
N = simulation_parameters$initial_state_values %>% sum()
error_median = with(rt_estimates, median(abs(rt.simple_mean_error), na.rm = T)) %>% signif(digits = 2)
error_quantile_975 = with(rt_estimates, quantile(abs(rt.simple_mean_error), 0.975, na.rm = T)) %>% signif(digits = 2) %>% format(scientific = F)
error_quantile_025 = with(rt_estimates, quantile(abs(rt.simple_mean_error), 0.025, na.rm = T)) %>% signif(digits = 2) %>% format(scientific = F)
```
